R for Clinical Study Reports and Submission

### 2021-10-12 submission-package.Rmd
add review comments

The files in two directories within the eCTD folder structure
are critical for documenting analysis using R: `datasets`
and `programs`. We assume the eCTD folder is `esub`.

```
/esub/analysis/adam/
├── datasets
│   ├── adrg.docx
│   ├── analysis-results-metadata.docx
│   ├── define-v1-updated-html.xsl
│   ├── define.pdf
│   └── define.xml
└── programs
    ├── tlf-01-disposition.txt
    ├── tlf-02-population.txt
    ├── tlf-03-baseline.txt
    ├── tlf-04-efficacy.txt
    ├── tlf-05-ae-summary.txt
    ├── tlf-06-ae-spec.txt
    └── r0pkgs.txt
```

@@

Folder path: `esub/analysis/adam/datasets/`.

- ADaM data in `.xpt` format: created by SAS
- `define.xml`: created by Pinnacle 21
- ADRG (ADaM Reviewer's Guide)
  - "Macro Programs" section: provide R and R package versions with a snapshot date
  - Appendix: provide step-by-step instructions for reviewers to
    reproduce the running environment and rerun analyses
- ARM (Analysis Results Metadata): provide the links between TLFs and
  analysis programs in tables

@@

Folder path: `esub/analysis/adam/programs/`.

- `r0pkgs.txt`: contains all internally developed R packages
- Other `.txt` files: each contains R code for a specific analysis

@@

Always use a consistent version of R for developing the TLFs and for submission.
For example, you could enforce a rule to only use R x.y.z where z = 1,
such as R 4.0.1 or R 4.1.1.
This can be automatically checked using a
[startup script](https://github.com/elong0527/esubdemo/blob/master/inst/startup.R)
when the R project is opened.

>>>>

In eCTD deliverable, the analysis dataset and source code are saved 
under the module 5 folder `m5/datasets/<study>/analysis/adam`.

For illustration and preparation purpose, we temporarily save
the under the `vignettes/esub/` folder.

The files in two directories within the `adam/` folder
are critical for documenting analysis using R: `datasets/`
and `programs/`.

```
vignettes/esub/analysis/adam/
├── datasets
│   ├── adrg.docx
│   ├── analysis-results-metadata.docx
│   ├── define-v1-updated-html.xsl
│   ├── define.pdf
│   └── define.xml
└── programs
    ├── tlf-01-disposition.txt
    ├── tlf-02-population.txt
    ├── tlf-03-baseline.txt
    ├── tlf-04-efficacy.txt
    ├── tlf-05-ae-summary.txt
    ├── tlf-06-ae-spec.txt
    └── r0pkgs.txt
```

@@

Folder path: `vignettes/esub/analysis/adam/datasets/`.

- ADaM data in `.xpt` format: created by SAS or R.
- `define.xml`: created by Pinnacle 21.
- ADRG (ADaM Reviewer's Guide)
  - "Macro Programs" section: provide R and R package versions with a snapshot date.
  - Appendix: provide step-by-step instructions for reviewers to
    reproduce the running environment and rerun analyses.
- ARM (Analysis Results Metadata): provide the links between TLFs and
  analysis programs in tables.

@@

Folder path: `vignettes/esub/analysis/adam/programs/`.

- `r0pkgs.txt`: contains all internally developed proprietary R packages.
- Other `.txt` files: each contains R code for a specific analysis.

@@

Always use a consistent version of R for developing the TLFs and for submission.
For example, you could enforce a rule to only use R `x.y.z` where `z = 1`,
such as R `4.0.1` or R `4.1.1`.
This can be automatically checked using a
[startup script](https://github.com/elong0527/esubdemo/blob/master/inst/startup.R)
when the R project is opened.
